---
title: "Horizon Stability Check"
format:
  html:
    toc: true
    toc-depth: 2
---

## Overview

We ran a single 1001-tick baseline (OFF only, seed=0) to validate the short-horizon settings outlined in `docs/blueprint.md`. For each manuscript metric we recomputed tail-window estimates using windows `T ∈ {120,160,200,240,280,320,360,400,500,750,1000}`. A window is considered stable when two consecutive step comparisons satisfy the tolerance rule from the blueprint addition (`τ = 5%`, except `τ = 2%` for average spreads).

## Stability summary

```{r}
library(readr)
hsc <- read_csv("../data/reference/hsc_summary.csv", show_col_types = FALSE)
hsc
```

Metrics that meet the tolerance rule by `T = 200` (inflation volatility, price dispersion, average spread, fill rate) confirm the existing A/B horizons. Credit growth and wage dispersion do not stabilise within 1 000 ticks; their series continue to trend, so keeping 200-tick snapshots would systematically understate their long-run behaviour.

## Convergence plots

```{r}
library(fs)
plots <- sort(dir_ls("../figs/reference", regexp = "hsc_convergence_.*\\.png$"))
knitr::include_graphics(plots)
```

## Next steps

* Manuscript horizons adopted: **A/B = 240**, **Scenarios = 250**, **Robustness = 120** (window = full run).
* Bank KPI swap: headline metrics are **average spread** and **loan-to-output ratio**; credit-growth remains as a robustness overlay.
* Wage and price dispersion now use the 240-tick window; their Quarto tables should cite the new horizon in captions.

All raw series are stored in `data/reference/hsc_series.json` for future inspection.
